Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda \\~

### 2013-03-11 Web3D2013-Dec3D/paper.tex
little reformatting

\subsection{X3DOM and XML3D}

With X3DOM \cite{Behr2009} and XML3D \cite{Sons2010} two open-source frameworks are available, which are briefly introduced in this section. Both frameworks support the ongoing discussion in the computer graphics and Web communities how an integration of HTML(5) and Declarative 3D content could look like. This discussion is followed by the presentation of the so-called ``polyfill'' approach for further development activities.

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\linewidth]{images/museum_with_tags2.pdf}
  \caption{A highly dynamic declarative 3D scene with nine animated and skinned characters. The calculation is either performed with classical sequential JavaScript or in parallel exploiting Intel's River Trail proposal for parallel data computations in JavaScript.}
  \label{fig:xflow}
  \vspace{-0.2cm}
\end{figure}

XML3D \cite{Sons2010} is a collaboration of DFKI and Intel VCI. Similar to X3DOM, it employs CSS3, DOM scripting, DOM events, and WebGL. In contrast to X3DOM, XML3D is designed as a extension to HTML5 from scratch. It does not define a scene-graph but uses the DOM tree structure for parent child relations and second level references e.g\ via CSS to (re-)use resources such as geometry data, material descriptions or animation data. These resources are not necessarily in the same document, but can also come from external documents in various formats, e.g. as JSON files.

@@

\subsection{Polyfill Approach}

% Don't cite this link but present the whole idea here!
% http://www.w3.org/community/declarative3d/wiki/Level_of_Integration/
We also propose to measure a level of integration for 3D graphics in terms of W3C technologies (DOM, CSS, etc.) to explain existing and possible integration levels (Figure \ref{fig:polyInt} shows that currently only level 2, DOM integration, is possible), and to finally identify a suitable integration level for declarative 3D. However, the latter imposes several problems in that it requires having a set of 3D-specific CSS properties or even a full shader description via CSS as well as a deeper integration into debugging tools like Chrome Developer Tools or Firebug. However, integration levels 3 and 4 are currently not yet achievable by a JavaScript implementation, because the required APIs are missing: it is not possible to introduce new CSS properties or to extend developer tools by an API.

>>>>

\subsection{X3DOM and XML3D}
With X3DOM \cite{Behr2009} and XML3D \cite{Sons2010} two open-source frameworks are available, which are briefly introduced in this section. Both frameworks support the ongoing discussion in the computer graphics and Web communities how an integration of HTML(5) and Declarative 3D content could look like. This discussion is followed by the presentation of the so-called ``polyfill'' approach for further development activities.

@@

\vspace{-1px}

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\linewidth]{images/museum_with_tags2.pdf}
  \caption{A highly dynamic declarative 3D scene with nine animated and skinned characters. The calculation is either performed with classical sequential JavaScript or in parallel exploiting Intel's River Trail proposal for parallel data computations in JavaScript.}
  \label{fig:xflow}
  \vspace{-0.3cm}
\end{figure}

\vspace{-1px}

XML3D \cite{Sons2010} is a collaboration of DFKI and Intel VCI. Similar to X3DOM, it employs CSS3, DOM scripting, DOM events, and WebGL. In contrast to X3DOM, XML3D is designed as a extension to HTML5 from scratch. It does not define a scene-graph but uses the DOM tree structure for parent child relations and second level references e.g\ via CSS to (re-)use resources such as geometry data, material descriptions or animation data. These resources are not necessarily in the same document, but can also come from external documents in various formats, e.g. as JSON. % files.

\vspace{-1px}

@@

\subsection{Polyfill Approach}
% Don't cite this link but present the whole idea here!
% http://www.w3.org/community/declarative3d/wiki/Level_of_Integration/
We also propose to measure a level of integration for 3D graphics in terms of W3C technologies (DOM, CSS, etc.) to explain existing and possible integration levels (Figure \ref{fig:polyInt} shows that currently only level 2, DOM integration, is possible), and to finally identify a suitable integration level for declarative 3D. However, the latter imposes several problems in that it requires having a set of 3D-specific CSS properties or even a full shader description via CSS as well as a deeper integration into debugging tools like Chrome Developer Tools or Firebug. However, integration levels 3 and 4 are currently not yet achievable by a JavaScript implementation, because the required APIs are missing: it is not possible to introduce new CSS properties or to extend developer tools by an API.
